---
title: "Kobe_Analysis"
author: "Pankaj Kumar"
date: "7/14/2019"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(caret)
library(reshape2)
library(car)
```


```{r, echo= FALSE , warning = FALSE}

kobe_data = readxl::read_excel('Analysis/Data/project2KobeData.xlsx' , sheet = 'modelData')

kobe_pred_data = readxl::read_excel('Analysis/Data/project2KobeData.xlsx', sheet = 'predData'  )

```


## Some observation on the data 

```{r}

length(kobe_data)
nrow(kobe_data)
ncol(kobe_data)
dim(kobe_data)

```


## check if there are any null or empty values are there

```{r, echo= FALSE , warning=FALSE }
sapply(kobe_data, function (x) {sum(x!="")}) != 20697

```

### Not null or missing

```{r, echo= FALSE , warning=FALSE }

sapply(kobe_data, function (x) {sum(is.na(x))}) != 0


```

### Transformations :


minutes remaining and second remaining can be compined to make a new variable called time remaining


```{r, echo= FALSE , warning=FALSE }

kobe_data = mutate(kobe_data, time_remaning= minutes_remaining+ seconds_remaining/60 ) 
```



# plots 

```{r, echo= FALSE , warning=FALSE }

p = ggplot(data= kobe_data) 

```


## Factors 

Graphs of all the variable with alphanumeric value.

### action_type

```{r, echo= FALSE , warning=FALSE }

p+
  geom_bar(mapping= aes(x=  action_type, fill = as.factor(shot_made_flag)))+
  coord_flip()
```


### combined_shot_type

```{r, echo= FALSE , warning=FALSE }


p+
  geom_bar(mapping= aes(x=  combined_shot_type, fill = as.factor(shot_made_flag)))+
  coord_flip()

```


### matchup

```{r, echo= FALSE , warning=FALSE }

  p+
    geom_bar(mapping= aes(x=  matchup, fill = as.factor(shot_made_flag)))+
    coord_flip()
   
```

### opponent

```{r, echo = FALSE , warning= FALSE}

  p+
    geom_bar(mapping= aes(x=  opponent, fill = as.factor(shot_made_flag)))+
    coord_flip()
```
 
### Season 

```{r, echo = FALSE , warning= FALSE}

  p+
    geom_bar(mapping= aes(x=  season, fill = as.factor(shot_made_flag)))+
    coord_flip()
```


### shot_type
```{r, echo = FALSE , warning= FALSE}

  p+
    geom_bar(mapping= aes(x=  shot_type, fill = as.factor(shot_made_flag)))+
    coord_flip()
```

### period
  
```{r, echo = FALSE , warning= FALSE}

  p+
    geom_bar(mapping= aes(x=  period, fill = as.factor(shot_made_flag)))
  
  p+
    geom_histogram(mapping= aes(x=  period, fill = as.factor(shot_made_flag)))
  coord_flip()
  
```
  
### playoffs 

```{r, echo = FALSE , warning= FALSE}

  p+
    geom_bar(mapping= aes(x=  playoffs, fill = as.factor(shot_made_flag)))+
    coord_flip()
  
  p+
    geom_histogram(mapping= aes(x=  playoffs, fill = as.factor(shot_made_flag)))
  coord_flip()
  
```


### shot_zone_area


```{r, echo = FALSE , warning= FALSE}

  p+
    geom_bar(mapping= aes(x=  shot_zone_area, fill = as.factor(shot_made_flag)))+
    coord_flip()
  
```

### shot_zone_basic

```{r, echo = FALSE , warning= FALSE}

  
  p+
    geom_bar(mapping= aes(x=  shot_zone_basic, fill = as.factor(shot_made_flag)))+
    coord_flip()

```

### shot_zone_range 

```{r, echo = FALSE , warning= FALSE}
  p+
    geom_bar(mapping= aes(x=  shot_zone_range, fill = as.factor(shot_made_flag)))+
    coord_flip()
  
  
```

## Numerical variables that can be treated as factors

### game_event_id  

```{r, echo = FALSE , warning= FALSE}


```


  
## Continuous var 

### game_event_id  

```{r, echo = FALSE , warning= FALSE}
  p+
    geom_bar(mapping= aes(x=  game_event_id, fill = as.factor(shot_made_flag)))+
    coord_flip()

```



### shot_distance  

```{r, echo = FALSE , warning= FALSE}
  p+
    geom_bar(mapping= aes(x=  shot_distance, fill = as.factor(shot_made_flag)))+
    coord_flip()

```
  

  
### lat

```{r , echo= FALSE , warning= FALSE}
  
  p+
    geom_bar(mapping= aes(x=  lat, fill = as.factor(shot_made_flag)))+
    coord_flip()
  
  p+
    geom_histogram(mapping= aes(x=  lat, fill = as.factor(shot_made_flag)))
  coord_flip()

```
 
### loc_x

```{r , echo= FALSE , warning= FALSE}

  
  p+
    geom_bar(mapping= aes(x=  loc_x, fill = as.factor(shot_made_flag)))+
    coord_flip()
  
  
  p+
    geom_histogram(mapping= aes(x=  loc_x, fill = as.factor(shot_made_flag)))
  coord_flip()

```
 
### loc_y  

```{r , echo= FALSE , warning= FALSE}

  p+
    geom_bar(mapping= aes(x=  loc_y, fill = as.factor(shot_made_flag)))+
    coord_flip()
  
  p+
    geom_histogram(mapping= aes(x=  loc_y, fill = as.factor(shot_made_flag)))
  coord_flip()
  
```

###  lon

```{r , echo= FALSE , warning= FALSE}

  
  p+
    geom_bar(mapping= aes(x=  lon, fill = as.factor(shot_made_flag)))+
    coord_flip()
  
  p+
    geom_histogram(mapping= aes(x=  lon, fill = as.factor(shot_made_flag)))
  coord_flip()
  
```

### minutes_remaining 

```{r , echo= FALSE , warning= FALSE}

  p+
    geom_bar(mapping= aes(x=  minutes_remaining, fill = as.factor(shot_made_flag)))+
    coord_flip()

  p+
    geom_histogram(mapping= aes(x=  minutes_remaining, fill = as.factor(shot_made_flag)))
  coord_flip()
  

```


### seconds_remaining 

```{r , echo= FALSE , warning= FALSE}

  
  p+
    geom_bar(mapping= aes(x=  seconds_remaining, fill = as.factor(shot_made_flag)))+
    coord_flip()
  p+
    geom_histogram(mapping= aes(x=  seconds_remaining, fill = as.factor(shot_made_flag)))
  

```
### game_date

```{r , echo= FALSE , warning= FALSE}
 
  p+
    geom_bar(mapping= aes(x=  as.Date(game_date, origin="1900-01-01"), fill = as.factor(shot_made_flag)))+
    coord_flip()
  p+
    geom_histogram(mapping= aes(x=  as.Date(game_date, origin="1900-01-01"), fill = as.factor(shot_made_flag)))
  
```


### attendance


```{r , echo= FALSE , warning= FALSE}

  p+
    geom_bar(mapping= aes(x=  attendance, fill = as.factor(shot_made_flag)))+
    coord_flip()
  p+
    geom_histogram(mapping= aes(x=  attendance, fill = as.factor(shot_made_flag)))
  
```

  
### arena_temp
  
```{r , echo= FALSE , warning= FALSE}

  
  
  p+
    geom_bar(mapping= aes(x=  arena_temp, fill = as.factor(shot_made_flag)))+
    coord_flip()
  p+
    geom_histogram(mapping= aes(x=  arena_temp, fill = as.factor(shot_made_flag)))

```

  
### avgnoisedb

```{r , echo= FALSE , warning= FALSE}

  p+
    geom_bar(mapping= aes(x=  avgnoisedb, fill = as.factor(shot_made_flag)))+
    coord_flip()
  p+
    geom_histogram(mapping= aes(x=  avgnoisedb, fill = as.factor(shot_made_flag)))

```

### Multicolineariy detection using VIF


```{r , echo= FALSE , warning= FALSE}


col_data = mutate(kobe_data, time_remaning= minutes_remaining+ seconds_remaining/60 ) %>%
  select(avgnoisedb, arena_temp, attendance, game_date,  lon,loc_y,loc_x,shot_distance,lat)

cordata = round(cor(col_data))

head(cordata)

melted_cormat <- melt(cordata)
head(melted_cormat)

ggplot(data = melted_cormat, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile()+
  geom_text(aes(Var2, Var1, label = value), color = "black", size = 4) +
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    axis.ticks = element_blank(),
    legend.justification = c(1, 0),
    legend.position = c(0.6, 0.7),
    legend.direction = "horizontal")+
  guides(fill = guide_colorbar(barwidth = 7, barheight = 1,
                               title.position = "top", title.hjust = 0.5))

vif(lm (lon ~ arena_temp*game_date*attendance, data = col_data))

kobe_data_for_log_model = mutate(kobe_data , locy = loc_y, cordx= loc_x) %>%
  select(-c(loc_y, loc_x))

log_mod_formula = shot_made_flag ~ avgnoisedb+ arena_temp+ attendance+ game_date + seconds_remaining +
  minutes_remaining + lon    + lat + game_event_id

logistic_model = glm (log_mod_formula,  data = kobe_data_for_log_model, family = "binomial")

alias(logistic_model)
vif(logistic_model)
```

### Outlier detection using cook's D value

```{r , echo= FALSE , warning= FALSE}

cooksd = cooks.distance(logistic_model)
plot(cooksd, pch="*", cex=2, main="Influential Obs by Cooks distance")  # plot cook's distance
abline(h = 4*mean(cooksd, na.rm=T), col="red")  # add cutoff line
text(x=1:length(cooksd)+1, y=cooksd, labels=ifelse(cooksd>4*mean(cooksd, na.rm=T),names(cooksd),""), col="red")

 
```

### Relation of shot made with distance and playoffs 

```{r , echo= FALSE , warning= FALSE}

p+
  geom_point(mapping =  aes(x= shot_distance, y =   as.factor(shot_made_flag)))

p+
  geom_histogram(mapping =  aes(x= shot_distance, fill = 
                                  as.factor( shot_made_flag)))+
  facet_wrap(.~playoffs)


```

